---
title: "EVT Score Audit"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(echo = FALSE)
opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)

wd <- rprojroot::find_rstudio_root_file()
opts_knit$set(root.dir = wd)
```

Script to check for inconsistencies in the EVT scores in the database.

```{r connect}
# Connect to db
library("L2TDatabase")
library("dplyr", warn.conflicts = FALSE)
cnf_file <- "inst/l2t_db.cnf"
l2t <- l2t_connect(cnf_file, "backend")
```

```{r}
# Combine child, study, childstudy, and evts tbls
evts <- tbl(l2t, "ChildStudy")  %>%
  left_join("Study" %from% l2t) %>%
  left_join("Child" %from% l2t) %>%
  left_join("EVT" %from% l2t) %>%
  # Download rows for kids with raw scores
  filter(!is.na(EVT_Raw)) %>%
  select(Study, ID = ShortResearchID, Birthdate, EVT_Form:EVT_Age) %>%
  collect()

# Download Form A norms
evt_norms <- l2t_connect(cnf_file, "norms") %>%
  tbl("EVT2") %>%
  collect()

# Make a form of the table amenable for score checking
norm_check <- evts %>%
  # Round age up to 30 months if younger than test norms
  mutate(Age = ifelse(EVT_Age < 30, 30, EVT_Age)) %>%
  rename(Raw = EVT_Raw, OurStnd = EVT_Standard, OurGSV = EVT_GSV) %>%
  select(-EVT_Age, -Birthdate, -EVT_Completion)
```



## Preliminary checks

### Missing Dates

```{r}
evts %>%
  filter(is.na(EVT_Completion)) %>%
  select(Study:EVT_Completion)
```


### Missing Forms

```{r}
evts %>%
  filter(is.na(EVT_Form)) %>%
  select(Study:EVT_Completion) %>%
  arrange(Study, ID) %>%
  as.data.frame()
```

### Ages

Recompute test ages and compare to age in EVT table

```{r}
evts %>%
  select(Study, ID, Birthdate, EVT_Completion, EVT_Age) %>%
  filter(!is.na(EVT_Completion)) %>%
  mutate(ChronoAge = chrono_age(Birthdate, EVT_Completion)) %>%
  filter(EVT_Age != ChronoAge) %>%
  select(-Birthdate)
```



## Derived Scores

### Form B scores

We cannot automatically check these scores because we only have the Form A
norms.

```{r}
norm_check %>% filter(EVT_Form == "B")
```

### Form A checks

```{r}
# Get norms for each Age, Raw Score
form_a <- norm_check %>%
  filter(EVT_Form %in% "A") %>%
  left_join(evt_norms) %>%
  select(Study:EVT_Form, NormAge = Age, Raw, OurStnd, Stnd, OurGSV, GSV)

```

#### GSVs

```{r}
form_a_gsv <- form_a %>% filter(OurGSV != GSV)
form_a_gsv
```

#### Standard Scores

```{r}
form_a_std <- form_a %>% filter(OurStnd != Stnd) %>% arrange(Study, ID)
form_a_std
```



### Form NA checks

Assume that all tests with missing forms are just Form A tests.

```{r}
form_na <- norm_check %>%
  filter(is.na(EVT_Form)) %>%
  left_join(evt_norms) %>%
  select(Study:EVT_Form, NormAge = Age, Raw, OurStnd, Stnd, OurGSV, GSV)
```

#### GSVs

```{r}
form_na_gsv <- form_na %>% filter(OurGSV != GSV)
form_na_gsv
```

#### Standard Scores

```{r}
form_na_std <- form_na %>% filter(OurStnd != Stnd) %>% arrange(Study, ID)
form_na_std
```



## Clean up

Save results to a csv.

```{r}
results <- bind_rows(form_na_gsv, form_na_std, form_a_std, form_a_gsv)

results <- data_frame(
  Check = "EVT",
  Date = format(Sys.Date()),
  Passing = nrow(results) == 0)

readr::write_csv(results, "./inst/audit/results_evt.csv")
```
