---
title: "Longitudinal Data Integrity Check"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(echo = FALSE)
opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
opts_knit$set(root.dir = "../../")
```

```{r gather data, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("L2TDatabase")
library("dplyr")
library("tidyr")
library("stringr")

# Load external dependencies
source("inst/paths.R")
source(paths$GetSiteInfo)
source("inst/migrations/dates.R")

# Collect dates/scores
df_dates <- collect_dates(paths$score_dates, recursive = TRUE)

df_no_visits <- df_dates %>% 
  filter(Variable == "Visited") %>% 
  select(-Variable) %>% 
  rename(Visited = Value) %>% 
  filter(Visited == FALSE)

columns_in_dirt <- df_dates %>% 
  select(Variable) %>% 
  distinct

# Columns used the 2 sites x 3 timepoints spreadsheets
unique(df_dates$Variable)

# Get T1 scores for both sites. Function sourced via paths$GetSiteInfo
t1 <- GetSiteInfo("ParticipantData_TimePoint1", separately = TRUE)
t2 <- GetSiteInfo("TimePoint2", separately = TRUE)
t3 <- GetSiteInfo("TimePoint3", separately = TRUE)

# Select necessary columns
get_scores_from_info <- function(df) {
  # Select and rename columns we want to compare
  df %>%
    select(ParticipantID = Participant_ID, Study,
           # use starts_with so that we don't get an error when the column is not found
           EVT_Form = starts_with("EVT_Form"),
           EVT_Date = starts_with("EVT_COMPLETION"),
           EVT_Raw = starts_with("EVT_raw"),
           EVT_Standard = starts_with("EVT_standard"),
           EVT_GSV = starts_with("EVT_GSV"),
           PPVT_Form = starts_with("PPVT_Form"),
           PPVT_Date = starts_with("PPVT_COMPLETION"),
           PPVT_Raw = starts_with("PPVT_raw"),
           PPVT_Standard = starts_with("PPVT_standard"),
           PPVT_GSV = starts_with("PPVT_GSV"),
           FruitStroop_Score = starts_with("fruitstroop_time"),
           VerbalFluency_Score = starts_with("verbalfluency_raw"),
           VerbalFluency_AgeEquivalent = starts_with("verbalfluency_AE"),
           CTOPPElision_Raw = starts_with("CTOPP_Elision_raw"),
           CTOPPElision_Scaled = starts_with("CTOPP_Elision_scaled"),
           CTOPPBlending_Raw = starts_with("CTOPP_Blending_raw"),
           CTOPPBlending_Scaled = starts_with("CTOPP_Blending_scaled"),
           CTOPPMemory_Date = starts_with("CTOPP_MemoryforDigits_COMPLETION"),
           CTOPPMemory_Raw = starts_with("CTOPP_MemoryforDigits_raw"),
           CTOPPMemory_Scaled = starts_with("CTOPP_MemoryforDigits_scaled"),
           KBIT_Raw = starts_with("Kbit_nonverbalraw"),
           KBIT_Standard = starts_with("Kbit_nonverbalstandard"),
           GFTA_Date = starts_with("GFTA_COMPLETION_DATE"),
           DELV_Date = starts_with("DELV_Date"),
           DELV_LanguageVar_ColumnAScore = starts_with("DELV_LanguageVar_ColumnAScore"),
           DELV_LanguageVar_ColumnBScore = starts_with("DELV_LanguageVar_ColumnBScore"),
           DELV_LanguageVar = matches("DELV_LanguageVar$"),
           DELV_LanguageRisk_DiagnosticErrorScore = starts_with("DELV_LanguageRisk_DiagnosticErrorScore"),
           DELV_LanguageRisk = matches("DELV_LanguageRisk$")) %>%
    # Add additional info
    mutate(
      Source = "ParticipantInfo") %>%
    # Set dates to strings
    mutate_each(funs(format), matches("Date"))
}

# Combine scores in the UMN/UW spreadsheets, convert to long format
normalize_sheets <- . %>% 
  lapply(get_scores_from_info) %>% 
  bind_rows %>% 
  gather(Variable, Value, -ParticipantID, -Study, -Source)

# Normalize data from all three studies, combine to single study
df_info_long <- list(t1, t2, t3) %>% 
  lapply(normalize_sheets) %>% 
  bind_rows

# Which columns need to be compared?
columns_in_info_sheets <- df_info_long %>% 
  select(Study, Variable) %>% 
  distinct

# Get the re-entered scores into the same format
df_dirt <- df_dates %>%
  select(-Site) %>%
  semi_join(columns_in_info_sheets) %>% 
  mutate(Source = "DIRT")

```

In Spring 2015, we had our data-entry team re-enter test scores gathered in the
longitudinal study, so that we could find data-entry discrepancies. This script
compares the original to the re-entered scores.



## Participant pool comparison

Do the same participants contribute scores in each set?

```{r}
df_both <- bind_rows(df_dirt, df_info_long)
df_sources_per_id <- df_both %>% 
  select(-Variable, -Value) %>% 
  distinct %>% 
  mutate(Found = TRUE) %>% 
  spread(Source, Found) %>% 
  arrange(Study, ParticipantID)
```

Participants in original score-set ("ParticipantInfo") *not in* the re-entered
score-set ("DIRT"):

```{r}
df_sources_per_id %>% 
  filter(is.na(DIRT)) %>% 
  anti_join(df_no_visits)
```

Participants in re-entered score-set ("DIRT") who visited the lab but are *not
in* the original score-set ("ParticipantInfo"). 

```{r}
df_sources_per_id %>% 
  filter(is.na(ParticipantInfo)) %>% 
  anti_join(df_no_visits)
```



## Value Comparison

We now compare the scores in each score-set. This check is only being performed
on participants in both score-sets.

```{r}
# Find which kids appear in both sources
df_children_to_compare <- df_sources_per_id %>% 
  filter(!is.na(DIRT), !is.na(ParticipantInfo)) %>% 
  select(Study, ParticipantID) %>% 
  distinct

df_comparing_scores <- df_both %>% 
  semi_join(df_children_to_compare) 

discrepancies <- df_comparing_scores %>%
  # select(-Study) %>%
  split(.$Variable) %>%
  lapply(readr::type_convert) %>%
  lapply(spread_, "Source", "Value") %>% 
  # lapply(function(df) select(df, DIRT)) %>%
  lapply(function(df) filter(df, DIRT %!==% ParticipantInfo)) %>%
  Filter(function(df) nrow(df) != 0, .) %>% 
  lapply(as.data.frame)
```

### Unchecked fields

The following columns in DIRT are not being checked because there is not a
matching column in the participant info spreadsheets

```{r}
columns_in_dirt %>% 
  anti_join(columns_in_info_sheets) %>% 
  filter(Variable != "DOB", Variable != "Visited") %>% 
  as.data.frame %>% 
  mutate(Status = ":grey_question:") %>% 
  rename(` ` = Status) %>% 
  kable
```


### Summary

This table lists all the fields that were checked and whether any discrepancies
were found in that field.

```{r}
columns_with_discrepancies <- discrepancies %>% names

columns_in_info_sheets %>% 
  select(Variable) %>% 
  distinct %>% 
  mutate(Passing = !(Variable %in% columns_with_discrepancies)) %>% 
  arrange(Variable) %>% 
  mutate(Status = ifelse(Passing, ":white_check_mark:", ":x:")) %>% 
  as.data.frame %>% 
  rename(` ` = Status) %>% 
  kable
```

### Details

These are all the mismatching values.

```{r}
discrepancies
```
