---
title: "Documentation Check"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE, echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(echo = TRUE)
opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
opts_knit$set(root.dir = "../../")
```

MySQL allows users to write short documentation comments for database tables
(up to 80 characters) and for database fields (up to 255 characters). These
documentation comments can be queried and retrieved like other data, so they
provide a handy way to store descriptive metadata.

This script checks for missing documentation in database. 

### Preliminaries

```{r Connect, include = TRUE, message = FALSE, warning = FALSE}
# Connect to the scores database
library("L2TDatabase")
library("dplyr")

cnf_file <- "inst/l2t_db.cnf"
l2t <- l2t_connect(cnf_file, "backend")
```

### We cannot document views

_Views_ are tables that are dynamically show the results of a query. These are
prefixed in the database with "q_" (for _query_). These view tables, and the
derived fields computer in them, cannot be documented. We have to ignore these
tables in our check

The following tables are views and can only have have limited documentation.

```{r}
describe_db(l2t) %>% 
  filter(Description == "VIEW")
```

In the `q_MinPair_Aggregate` view, the proportion correct for non-training
trials is a derived value. The field `MinPair_ProportionCorrect` is created
and computed as the query is executed. Therefore, there is no documentation
available for it.

```{r}
l2t %>% 
  describe_tbl("q_MinPair_Aggregate") %>% 
  filter(Description == "")
```



## Undocumented Tables

The following tables are missing documentation:

```{r}
no_table_doc <- describe_db(l2t) %>% filter(Description == "")
no_table_doc
```

## Undocumented Fields

The following fields are missing documentation.

```{r}
# Omit strings containing a pattern
str_reject <- function(string, pattern) { 
  string[!stringr::str_detect(string, pattern)]
}

non_view_tbls <- src_tbls(l2t) %>% str_reject("q_")

# Get description of each non-view table. Combine them.
all_descriptions <- Map(function(x) describe_tbl(l2t, x), non_view_tbls) %>% 
  bind_rows() %>% 
  as_data_frame()

# Keep only undocumented rows
undocumented_fields <- all_descriptions %>% 
  # Ignore the temporary tables used for mass data-entry
  mutate(IsEntryTable = stringr::str_detect(Table, "_Entry")) %>% 
  filter(Description == "", !IsEntryTable) %>% 
  select(Table, Field, Description) %>% 
  print(n = Inf)
undocumented_fields
```

## Name checks

We need to be careful about tables that share field names because they will
not join correctly. For example, trying to combine an Experiment table with a
`Dialect` column to a ParticipantInfo table with `Dialect` column will wrongly
combine experiments and children that share the same values in the Dialect
column. Which is not what we want, especially the same child is exposed to
different versions of an experiment with different dialects. 

Ideally, only index fields should be allowed to appear in more than one table, 
and we check that this is the case. We allow tables for item-level data to have 
repeated names (like Trial or Stimulus1), so we ignore tables with `_Responses`
in the name.

```{r}
# Get description of each non-view table. Combine them.
repeated_names <- all_descriptions %>% 
  # Ignore the temporary tables used for mass data-entry
  mutate(IsEntryTable = stringr::str_detect(Table, "_Entry"),
         IsItemTable = stringr::str_detect(Table, "_Responses")) %>% 
  filter(Index == "", !IsEntryTable, !IsItemTable) %>% 
  # Count the occurrence of each field
  group_by(Field) %>% 
  mutate(FieldCount = length(Field)) %>% 
  ungroup() %>% 
  # Keep duplicated fields
  filter(FieldCount != 1) %>% 
  select(Field, Table) %>% 
  arrange(Field) %>% 
  print(n = Inf)
repeated_names
```



```{r, echo = FALSE}
results <- bind_rows(repeated_names, undocumented_fields, no_table_doc)
results <- data_frame(
  Check = "MySQL metadata",
  Date = format(Sys.Date()),
  Passing = nrow(results) == 0
)
readr::write_csv(results, "./inst/audit/results_metadata.csv")
```




