---
title: "L2TDatabase"

output: 
  github_document:
    toc: true
    toc_depth: 2

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warning = FALSE}
library("dplyr", warn.conflicts = FALSE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

# Override dplyr print methods to obscure the server address
print.tbl_sql <- function(x, ..., n = NULL, width = NULL) {
  cat("Source:   query ", dim_desc(x), "\n", sep = "")
  x2 <- x
  x2$src$info$user <- "demo_user"
  x2$src$info$host <- "dummy.host.name"
  
  cat("Database: ", src_desc(x2$src), "\n", sep = "")
    grps <- op_grps(x$ops)
    if (length(grps) > 0) {
        cat("Groups: ", commas(op_grps(x$ops)), "\n", sep = "")
    }
    cat("\n")
    print(trunc_mat(x, n = n, width = width))
    invisible(x)
}
```





This R package contains helper functions for working with the MySQL database for
the [Learning To Talk](http://learningtotalk.org) project.


Installation
-------------------------------------------------------------------------------

Install the `devtools` package. Then install the package from GitHub.

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("LearningToTalk/L2TDatabase")
```




Connecting with .cnf files
-------------------------------------------------------------------------------

Connections to the database are managed by [.cnf files][cnf-ref]. We use these 
files so that login credentials and connection information are not hard-coded 
into analysis scripts. 

This package provides the helper function `make_cnf_file()` which creates a .cnf
file from login and connection information. Once the file is created, we can
just point to this file whenever we want to connect to the database.

```{r, results = 'hide'}
library("L2TDatabase")

# initialze a cnf file using all default (empty) values
make_cnf_file(dest = "./my_connection.cnf")

# all values filled
make_cnf_file(
  dest = "./my_connection.cnf", 
  user = "tj", 
  password = "dummy-password", 
  db = "my_db", 
  host = "localhost", 
  port = 3306)
```

We use the function `l2t_connect()` to connect to the database. This function
takes the location of a .cnf file and the name of the database and returns
a connection to the database. By default, `l2t_connect` connects to the `l2t`
database.

```{r, results = 'hide'}
# connect to the database
l2t <- l2t_connect(cnf_file = "./inst/l2t_db.cnf", db_name = "l2t")
```




Using dplyr to look at the database
-------------------------------------------------------------------------------

This package is built on top of [dplyr][dplyr-page], a package for dealing with
data stored in tables. dplyr provides a set of tools for working with remote
data sources --- that is, data in databases, usually on other computers. 
Conventionally, to access data in a database, one has to write special queries
to retrieve information from the database. dplyr lets us write R code for our
queries, and it translates our R code into the language used by the database.
(See the dplyr [vignette on databases][dplyr-db] for more information on how to 
work with remotely stored data using dplyr.) 

In the terminology of dplyr, a remote _source_ of data is a `src`, and a _table_
of data is a `tbl`. To connect to a table of data, use `tbl(src, tbl_name)`.
For example, here's how I would connect to the `MinPair_Trials` table in the
database which contains the trial-level data about the minimal pairs experiment.

```{r}
library("dplyr", warn.conflicts = FALSE)

# use tbl to create a link to a tbl in the database
minp_resp <- tbl(src = l2t, from = "MinPair_Trials") 
minp_resp
```

With dplyr, I can perform all kinds of operations on this table. Here, I
`filter()` rows to keep just the _man_-_moon_ practice trials and `select()` a
subset of columns.

```{r}
man_moon_practice <- minp_resp %>% 
  filter(MinPair_Item1 == "man", MinPair_Item2 == "moon") %>% 
  select(Study, ResearchID, MinPair_TargetItem, MinPair_Correct)
man_moon_practice
```

This data lives in "the cloud" on a remote computer. That's why the first line
of the print out says `Source: query [?? x 4]`. When we print the data as we
did above, dplyr downloads just enough rows of data to give us a preview of
the data. There are approximately 12,000 rows of data in the `minp_resp` table,
and this just-a-preview behavior prevented us from accidentally or prematurely
downloading thousands of rows when we peeked at the data. We have to 
**use `collect()` to download data to our computer**.

```{r}
man_moon_practice <- collect(man_moon_practice)
man_moon_practice
```

In this printout, there is no longer a line specifying the source. Instead, we
are told that we have a `tibble`, which is just a kind of data-frame. The data
now lives locally, in our R session. Now, we can plot or model this data like
any other data-frame in R.

**Take-away**: We use dplyr to create queries for data from tables in a
database, and we use `collect()` download the results of the query to our
computer.




L2T Database conventions
-------------------------------------------------------------------------------

### User-ready data lives in the default database `l2t`

Information about our participants and their testing data are stored in two
separate databases. The first is `l2t`. This database contains user-friendly,
analysis-ready tables of information. `l2t` is the default database that
`l2t_connect()` uses. This database probably has the information that you need
in a ready to use form.

```{r}
# list all the tbls in the database
src_tbls(l2t)
```

The tables here are _queries_: Tables that are computed on-the-fly whenever the
data is requested. For example, `MinPair_Aggregate` shows the proportion correct
of non-practice trials in the minimal pairs task by participant and by study. (I
`select()` a subset of columns to exclude unnecessary columns like the name of
the Eprime file containing the raw data.) The `Study` and `ResearchID` are the
conventional identifiers for studies and participants.

```{r, warning = FALSE}
tbl(l2t, "MinPair_Aggregate") %>% 
  select(Study, ResearchID, MinPair_Dialect, MinPair_ProportionCorrect)
```

The values in `MinPair_ProportionCorrect` are not stored or hard-coded but
computed on the fly as part of a query. Thus, if for some reason, the 
trial-level data about the experiment were to change in the database, then the
`MinPair_ProportionCorrect` column would update automatically.


### Raw data lives in `backend`

The tables in `l2t` are queries, so they are assembled by combining information
from tables of raw data. The raw-data tables live in the second database (the
`backend` for our queries.) These raw data tables do not contain any of our
participant IDs or study names, so they are not user-friendly. You probably
don't need to work with the backend of the database, unless you are developing
new aggregations of data that are not yet presented in the `l2t` database.

```{r}
l2t_backend <- l2t_connect("./inst/l2t_db.cnf", db_name = "backend")
# list all the tbls in the database
src_tbls(l2t_backend)
```

Some of the tables in the backend are not tables of raw data but
intermediate, helper queries that are used in the main database. These
helpers queries are prefixed with `q_`. For example, `q_Household_Education`,
`q_Household_Maternal_Caregiver`, and `q_Household_Max_Maternal_Education` are a
pipeline of calculations that determine the highest maternal education level in
each household.


### Other databases

Our eyetracking data lives in `eyetracking`. I separated it from the other kinds
of data because it contains individual frames of eyetracking data, so it houses
a tremendous amount of data. One of the tables has at least 10 millions rows of
data. The database contains user-ready queries. They are prefixed by `q_`.

```{r}
l2t_eyetracking <- l2t_connect("./inst/l2t_db.cnf", db_name = "eyetracking")
src_tbls(l2t_eyetracking)
```

There is also a database `norms` with some raw-score-to-standardized-score
look-up tables for some standardized tests. 

**Take-away**: The data you probably want lives in the default database `l2t`.




Metadata
-------------------------------------------------------------------------------

As I've worked on the back-end of the database, I've been using the database
comments to describe the data that goes into each table and each field. We can
download these comments along with other pieces of information about a table by
using `describe_tbl()`. With this function, we can quickly create a "codebook" 
to accompany our data. 

```{r}
describe_tbl(src = l2t, tbl_name = "MinPair_Aggregate")
```

In some queries, the fields are computed dynamically, whenever the data
is requested. In the `MinPair_Aggregate` query, the proportion correct is
calculated when the data is requested. Our database system does not let us write
comments for these dynamically created columns, so that column has a blank for
its description. 

We can also download the table-level comments from a database with
`describe_db()`, although these descriptions have a much tighter length limit.
Table-level comments are also unavailable for query tables, so they are only
useful for raw-data tables.

```{r}
# just a few rows
describe_db(src = l2t_backend) %>% head()
```

These two forms of metadata are backed up by the `l2t_backup()` helper function.




Back up
-------------------------------------------------------------------------------

We can download and back up each table in a database with `l2t_backup()`. The
final two messages from the back-up function show that the metadata tables are
saved to a `metadata` folder.

Here's how backing up the backend of the database looks:

```{r, warning = FALSE}
# back up each tbl
backup_dir <- "./inst/backup"
all_tbls <- l2t_backup(src = l2t_backend, backup_dir = backup_dir)

# l2t_backup() also returns each tbl in a list, so we can view them as well.
all_tbls$EVT
```


### Dumping the database

A final option for backing up the database is `dump_database()`. This function
calls on the `mysqldump` utility which exports a database into a series of SQL
statements that can be used to reconstruct the database. This function is very 
finicky because it requires other programs to be installed on one's machine.

```{r, eval = FALSE}
dump_database(
  cnf_file = "./inst/l2t_db.cnf", 
  backup_dir = "./inst/backup",
  db_name = "l2t")

dump_database(
  cnf_file = "./inst/l2t_db.cnf", 
  backup_dir = "./inst/backup",
  db_name = "backend")
```




Writing new data to a database
-------------------------------------------------------------------------------

dplyr provides read-only access to a database, so we can't accidentally do
stupid things to our data. We want to use R to migrate existing dataframes into
the database, but we also don't want to do stupid things either. Therefore, I've
developed conservative helper functions for writing data. These functions work
on dplyr-managed database connections. For the purposes of this demo, we will
work on the separate `l2t_test` database.

The function `append_rows_to_table()` simply adds new rows to a database table.

```{r}
l2t_test <- l2t_connect("./inst/l2t_db.cnf", db_name = "l2ttest")

# Before writing
tbl(l2t_test, "TestWrites")

# Add rows to table
append_rows_to_table(
  src = l2t_test, 
  tbl_name = "TestWrites", 
  rows = data_frame(Message = "Hello!"))

# After writing
tbl(l2t_test, "TestWrites")
```

I also have an _experimental_ helper function. `overwrite_rows_in_table()`
which will update existing rows in a table, but this one is not as robust or
user-friendly as I would like. In my scripts, I usually have lots of checks
on the data before and after using this function to confirm that it behaves as
expected.

```{r clean up, echo = FALSE, results = 'hide'}
DBI::dbSendQuery(l2t_test$con, "DELETE FROM `l2ttest`.`TestWrites`")
file.remove("./my_connection.cnf")
```




Other helpers
-------------------------------------------------------------------------------

This package also provides some helper functions for working with our data.
`undo_excel_date()` converts Excel's dates into R dates. `chrono_age()` computes
the number of months (rounded down) between two dates, as you would when
computing chronological age.

```{r}
# Create a date and another 18 months later
dates <- list()
dates$t1 <- undo_excel_date(41659)
dates$t2 <- undo_excel_date(41659 + 365 + 181)
str(dates)

# Chrono age in months, assuming t1 is a birthdate
chrono_age(dates$t2, dates$t1)

# More chrono_age examples
chrono_age("2014-01-20", "2012-01-20")
chrono_age("2014-01-20", "2011-12-20")
chrono_age("2014-01-20", "2011-11-20")
```




Repository structure
-------------------------------------------------------------------------------

This repository is an R package, so the `R/`, `man/` and `tests/` contain
the source code, documentation, and unit tests for the package. 

Most of the action is in the `inst/` directory. `inst/migrations/` contains
R scripts that add data from our various spreadsheets and csv files to
the database. `inst/audit/` contains some helper scripts that check for
inconsistencys in our data. `inst/views/` contains the source code for our SQL
queries used by the database.



Data audits
-------------------------------------------------------------------------------

We have some scripts that audit our data-sets. The results of these checks are
printed here.

```{r, echo = FALSE, message = FALSE}
evt <- readr::read_csv("./inst/audit/results_evt.csv") %>% 
  mutate(Link = "[EVT](inst/audit/audit_evt.md)")
ppvt <- readr::read_csv("./inst/audit/results_ppvt.csv") %>% 
  mutate(Link = "[PPVT](inst/audit/audit_ppvt.md)")
integrity <- readr::read_csv("./inst/audit/results_integrity.csv") %>% 
  mutate(Link = "[Data entry discrepancies](inst/audit/check_integrity.md)")
docs <- readr::read_csv("./inst/audit/results_metadata.csv") %>% 
  mutate(Link = "[MySQL metadata completeness](inst/audit/check_documentation.md)")

checks <- bind_rows(evt, ppvt, integrity, docs) %>% 
  mutate(Result = ifelse(Passing, ":white_check_mark:", ":x:")) %>% 
  select(Check, Date, Passing, Result, Link)
knitr::kable(checks)
```



Study coverage
-------------------------------------------------------------------------------

The following table summarizes how many scores/administrations of each task
were collected for each study. It is included here to show which tasks and which
studies have been migrated into the database.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
tbls_to_check <- c(
  BRIEF = "BRIEF", 
  Blending = "Blending_Summary", 
  CTOPP_Memory = "CTOPP_Memory",
  CTOPP_Blending = "CTOPP_Blending",
  CTOPP_Elision = "CTOPP_Elision",
  DELV_Risk = "DELV_Risk",
  DELV_Variation = "DELV_Variation",
  EVT = "EVT", 
  FruitStroop = "FruitStroop", 
  GFTA = "GFTA", 
  KBIT = "KBIT",
  LENA = "LENA_Averages", 
  MinPair = "MinPair_Aggregate", 
  PPVT = "PPVT", 
  Rhyming = "Rhyming_Aggregate", 
  SAILS = "SAILS_Aggregate", 
  VerbalFluency = "VerbalFluency")

count_studies <- function(tbl_name, db = l2t) {
  responses <- tbl(db, tbl_name) %>% 
    collect() %>% 
    select(everything(), Date = ends_with("Completion")) %>% 
    filter(!is.na(Date))
  
  count_responses(responses)
}

count_responses <- . %>% 
    group_by(Study) %>% 
    summarise(Participants = n_distinct(ResearchID), 
              Administrations = n()) %>% 
    select(Study, Participants, Administrations)

study_counts <- tbls_to_check %>% 
  lapply(count_studies) 

# Count eyetracking administrations too
db_et <- l2t_connect("./inst/l2t_db.cnf", "eyetracking")
et_blocks <- tbl(db_et, "Blocks") %>% 
  left_join(tbl(db_et, "q_BlocksByStudy")) %>% 
  select(Study, ResearchID, Task, Block_Basename) %>% 
  collect() %>% 
  mutate(Task = paste0("Eyetracking: ", Task))

et_counts <- et_blocks %>% 
  split(.$Task) %>% 
  lapply(count_responses) 

df_counts <- c(study_counts, et_counts) %>% 
  bind_rows(.id = "Table") %>% 
  arrange(Table, Study)

knitr::kable(df_counts)
```





[cnf-ref]: http://svitsrv25.epfl.ch/R-doc/library/RMySQL/html/RMySQL-package.html
[dplyr-db]: http://cran.r-project.org/web/packages/dplyr/vignettes/databases.html
[blog-backup]: http://tjmahr.com/post/127080928329/using-dplyr-to-back-up-a-mysql-database
[dplyr-page]: https://cran.rstudio.com/web/packages/dplyr/
