---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# L2TDatabase

This R package contains helper functions for working with MySQL database for the
[Learning To Talk](http://learningtotalk.org) project. 

Connections to the database are managed by [.cnf files][cnf-ref]. This
package provides `make_cnf_file` which creates a cnf file from login and
connection information.

```{r, results = 'hide'}
library("L2TDatabase")

# initialze a cnf file using all default (empty) values
make_cnf_file()

# all values filled
make_cnf_file(dest = "my_connection.cnf", user = "tj", password = "", 
              db = "my_db", host = "localhost", port = 3306)
```

```{r, echo = FALSE, results = 'hide'}
file.remove("db.cnf")
file.remove("my_connection.cnf")
cnf_file <- file.path(getwd(), "inst/l2t_db.cnf")
```

Once we've create a .cnf file, we can now connect to the database using 
`l2t_connect`. We can view the names of all the tables in the database with 
`dplyr::src_tbls`. See the dplyr [vignette on databases][dplyr-db] for how to
work with remotely stored data using dplyr; it's really great stuff.

```{r}
library("dplyr", warn.conflicts = FALSE)

# connect to the database
l2t <- l2t_connect(cnf_file)

# list all the tbls in the database
src_tbls(l2t)

# use tbl to create a link to a tbl in the database
studies <- tbl(src = l2t, "Study") 
head(studies)
```

We can download and backup each table in the database with `l2t_backup`.

```{r}
# backup each tbl
backup_dir <- "inst/backup"
all_tbls <- l2t_backup(l2t, backup_dir)

# l2t_backup also returns each tbl in a list, so we can view them as well.
all_tbls$Study
```


[cnf-ref]: http://svitsrv25.epfl.ch/R-doc/library/RMySQL/html/RMySQL-package.html
[dplyr-db]: http://cran.r-project.org/web/packages/dplyr/vignettes/databases.html
