---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, echo = FALSE, results = 'hide'}
cnf_file <- file.path(getwd(), "inst/l2t_db.cnf")
```


# L2TDatabase

This R package contains helper functions for working with the MySQL database for
the [Learning To Talk](http://learningtotalk.org) project.

Connections to the database are managed by [.cnf files][cnf-ref]. This
package provides `make_cnf_file` which creates a cnf file from login and
connection information.

```{r, results = 'hide'}
library("L2TDatabase")

# initialze a cnf file using all default (empty) values
make_cnf_file()

# all values filled
make_cnf_file(dest = "my_connection.cnf", user = "tj", password = "", 
              db = "my_db", host = "localhost", port = 3306)
```

Once we've create a .cnf file, we can connect to the database using 
`l2t_connect`. We can view the names of all the tables in the database with 
`dplyr::src_tbls`. See the dplyr [vignette on databases][dplyr-db] for how to 
work with remotely stored data using dplyr; it's really great stuff.

```{r}
library("dplyr", warn.conflicts = FALSE)

# connect to the database
l2t <- l2t_connect(cnf_file)

# list all the tbls in the database
src_tbls(l2t)

# use tbl to create a link to a tbl in the database
studies <- tbl(src = l2t, "Study") 
head(studies)
```

We can download and backup each table in the database with `l2t_backup`.

```{r}
# backup each tbl
backup_dir <- "inst/backup"
all_tbls <- l2t_backup(l2t, backup_dir)

# l2t_backup also returns each tbl in a list, so we can view them as well.
rows <- lapply(all_tbls, nrow)
data_frame(tbl = names(rows), rows = unlist(rows))

all_tbls$ChildStudy
```

## Writing

dplyr provides read-only access to a database, so we can't accidentally do 
stupid things to our data. In order to write to the database in R, we have use
the interface provided by the package RMySQL. We connect to the database using 
`l2t_connect_writer`. For the purposes of this demo, we will work on the 
separate `l2t_test` database.

```{r}
library("RMySQL")
l2t_write <- l2t_writer_connect(cnf_file, db_name = "l2ttest")

# Table listing
dbListTables(l2t_write)

# Before writing
dbReadTable(l2t_write, "TestWrites")

# Add rows to table
append_rows_to_table(
  db_con = l2t_write, 
  tbl_name = "TestWrites", 
  rows = data_frame(Message = "Hello!"))

# After writing
dbReadTable(l2t_write, "TestWrites")
```

```{r clean up, echo = FALSE, results = 'hide'}
dbSendQuery(l2t_write, "DELETE FROM `l2ttest`.`TestWrites`")
file.remove("db.cnf")
file.remove("my_connection.cnf")
```



[cnf-ref]: http://svitsrv25.epfl.ch/R-doc/library/RMySQL/html/RMySQL-package.html
[dplyr-db]: http://cran.r-project.org/web/packages/dplyr/vignettes/databases.html
