---
title: "Finding normal-hearing matches for children with cochlear implants"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(
  warning = FALSE,
  collapse = TRUE, 
  comment = "#>", 
  message = FALSE,
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "80%")

wd <- rprojroot::find_rstudio_root_file()
opts_knit$set(root.dir = wd)
```


```{r}
library(dplyr)
library(L2TDatabase)

# Work relative to RStudio project
wd <- rprojroot::find_rstudio_root_file()
dir_here <- file.path(wd, "inst", "analyses", "ci_matching")
cnf_file <- file.path(wd, "inst", "l2t_db.cnf")
```

Starting pool for matching, the children at TimePoint1 without cochlear
implants, who are not late talkers and who speak mainstream American-English.

```{r}
l2t_main <- l2t_connect(cnf_file, "l2t")

nh_set1 <- tbl(l2t_main, "Scores_TimePoint1") %>% 
  filter(!AAE, !LateTalker, !CImplant, 
         !is.na(Maternal_Education), 
         !is.na(EVT_Standard)) %>% 
  collect()


nh_set2 <- tbl(l2t_main, "Scores_CochlearMatching") %>% 
  filter(!AAE, !LateTalker, !CImplant, 
         !is.na(Maternal_Education), 
         !is.na(EVT_Standard)) %>% 
  collect()

nh_set <- bind_rows(nh_set1, nh_set2)
```

Post-stratify by maternal education. First, define low-mid-high medu groups.

```{r}
medu_scheme <- data_frame(
  Maternal_Education_Level = c(NA, 1:7),
  Maternal_Education_Group = c(NA, "Low", "Low", "Low", "Low", 
                               "Mid", "Mid", "High")
)

nh_set %>% 
  left_join(medu_scheme) %>% 
  count(Maternal_Education, Maternal_Education_Level, 
           Maternal_Education_Group) %>% 
  arrange(Maternal_Education_Level)
```

Find the vocabulary scores that would define the 10-90% range for each maternal
education group.

```{r}
nh_vocab_limits <- nh_set %>% 
  left_join(medu_scheme) %>% 
  group_by(Maternal_Education_Group) %>% 
  summarise(
    n = n(),
    EVT_Mean = mean(EVT_Standard),
    EVT_Min = min(EVT_Standard), 
    EVT_Max = max(EVT_Standard),
    EVT_10 = quantile(EVT_Standard, .1),
    EVT_90 = quantile(EVT_Standard, .9),
    nInRange = sum(between(EVT_Standard, EVT_10, EVT_90))) %>% 
  ungroup()

nh_vocab_limits
```

Restrict pool to just children with scores in their range.

```{r}
nh_set %>% 
  left_join(medu_scheme) %>% 
  left_join(nh_vocab_limits) %>% 
  rowwise() %>% 
  mutate(InRange = between(EVT_Standard, EVT_10, EVT_90)) %>% 
  ungroup() %>% 
  filter(InRange)
```

