---
title: "Normalizing Eyetracking Data"
author: "Tristan Mahr"
date: "October 22, 2015"
output: 
  html_document: 
    keep_md: yes
---

## Gameplan

Our goal today is to prepare our eyetracking data to be inserted into a
database.

For database normalization, we want there to be five tables:

* Experiments: 1 row per administration of experiment.
* Trials: 1 row per trial of an eye-tracking experiment.
* Frames: 1 row per frame of eyetracking data in a trial.
* ExperimentsInfo: 1 row per attribute of a experiment
* TrialInfo: 1 row per attribute of a trial

The first three tables are meant to be nice and nested "wide" dataframes. We 
have looks nested in trials nested in experiment administrations, and each row 
is one thing (a frame, a trial, an experiment). These three tables are
experiment agnostic.

The other tables are meant to be a grab-bag of key-value pairs, containing 
things like the target word of each trial or the dialect of the experiment 
administration. These will be "long" dataframes, such that there are multiple 
rows for a single trial or experiment. The specific attributes that 
differentiate trials and experiments live in these tables. These tables will
allow the other three to be completely task agnostic.

## Eyetracking data from lookr

Use lookr to load and reduce some eye-tracking data.

```{r, warning = FALSE, message = FALSE}
library("lookr")
library("purrr")
library("knitr")
library("dplyr")
opts_chunk$set(comment = "#>", collapse = TRUE)
```


```{r}
# Load some example data bundled in lookr
mp_long <- file.path(find.package("lookr"), "docs/data/MP_WFFArea_Long/")
trials <- suppressMessages(Task(mp_long))
trials

# Light preprocessing: Set time 0 to target onset, map gaze locations to AOIs,
# interpolate spans of missing data up to 150ms in duration
trials <- AdjustTimes(trials, "TargetOnset")
trials <- AddAOIData(trials)
trials <- InterpolateMissingFrames(trials)
```

Note that each `Trial` object is just `data.frame` with several associated
`attributes`.

```{r}
print(trials[[1]], width = 80, strict.width = "wrap")
```

Extracting just the data-frame parts and combining them will provide us with the
rows for the Frames table. The Experiments/Trials rows will come from the
attributes. 

To link trials to administrations, we will create a new attribute `TrialName`
attibute that will uniquely identify trials.

```{r}
# Uniquely name each trial
trials %@% "TrialName" <- 
  sprintf("%s_%02.0f", trials %@% "Basename", trials %@% "TrialNo")
```

## Creating the wide tables

Now we can create the three main "wide" (task-invariant) tables. We `Basename`
to link experiment administrations to `TrialName` and `TrialName` to link to
eye-tracking frames.

```{r}
tbl_exps <- trials %>% 
  gather_attributes(c("Basename", "DateTime", "Subject", "Task")) %>% 
  as_data_frame %>% 
  distinct
tbl_exps

tbl_trials <- trials %>% 
  gather_attributes(c("TrialName", "Basename", "TrialNo")) %>% 
  as_data_frame %>% 
  distinct
tbl_trials

# Make a function that extracts the columns of gaze data from a Trial, then 
# apply it to each Trial
collect_looks <- function(x) {
  x_name <- x %@% "TrialName"
  # c(x) to strip attributes
  x <- c(x) %>% 
    as_data_frame %>% 
    mutate(TrialName = x_name) %>% 
    select(TrialName, Time, XMean, YMean, GazeByImageAOI, GazeByAOI)
  x
}

looks <- trials %>% map(collect_looks) %>% bind_rows

# Convert screen proportions to pixel locations
tbl_looks <- looks %>% 
  mutate(XMean = round(XMean * lwl_constants$screen_width),
         YMean = round(YMean * lwl_constants$screen_height))
tbl_looks
```


## Creating the grab-bag tables

### Prepare experimental grab-bag and flatten AOI definitions

Now we need to make the grab-bags of trial and experiment attributes. But first
let's unpack the implicit AOI definitions used in the experiments.

```{r}
library("tidyr")
library("stringr")

# hard-coded inside lookr:::GetImageAOI
AOIs <- list(
  UpperLeftImage = list(x_pix = c(410, 860), y_pix = c(700, 1150)), 
  LowerLeftImage = list(x_pix = c(410, 860), y_pix = c(50, 500)), 
  UpperRightImage = list(x_pix = c(1060, 1510), y_pix = c(700, 1150)), 
  LowerRightImage = list(x_pix = c(1060, 1510), y_pix = c(50, 500)), 
  FixationImage = list(x_pix = c(885, 1035), y_pix = c(525, 675)), 
  ImageL = list(x_pix = c(100, 700), y_pix = c(300, 900)), 
  ImageR = list(x_pix = c(1220, 1820), y_pix = c(300, 900)))

# Break apart names from unlist(...) into separate columns
aoi_table <- unlist(AOIs) %>% 
  data_frame(Image = names(.), Pixel = .) %>% 
  separate(Image, into = c("AOI", "Dimension", "Number")) %>% 
  mutate(Number = str_replace(Number, "pix", ""),
         AOIBoundary = "AOI_Boundary")
  
# Keep only values used in the data and combine columns into Key, Value
aoi_table <- aoi_table %>% 
  filter(AOI %in% unique(looks$GazeByAOI)) %>% 
  unite(col = AOI_Boundary, AOIBoundary, AOI:Number) %>% 
  rename(Key = AOI_Boundary, Value = Pixel)
aoi_table
```

Now we assembly the experiment key-value grab-bag and attach the AOI definitions.

```{r}
# Gather experiment attributes
tbl_exps_gb <- trials %>% 
  gather_attributes(c("Basename", "Dialect", "Protocol")) %>% 
  as_data_frame %>% 
  distinct %>% 
  # Other hard-wired constants
  mutate(FrameRate = lwl_constants$ms_per_frame,
         ScreenWidth = lwl_constants$screen_width,
         ScreenHeight = lwl_constants$screen_height) %>% 
  gather(key = Key, value = Value, -Basename) 

# Create all combinations of basename and AOI property name
aoi_rows <- list(Basename = tbl_exps$Basename, Key = aoi_table$Key) %>% 
  cross_n %>% 
  bind_rows %>% 
  left_join(aoi_table) %>% 
  mutate(Value = as.character(Value))
aoi_rows

# Combine AOI attributes with other ones
tbl_exps_attrs <- bind_rows(tbl_exps_gb, aoi_rows) %>% 
  arrange(Basename, Key)
tbl_exps_attrs
```

### Prepare trial grab-bag

Now we can do the trials attributes.

```{r}
trial_attrs <- 
  c("TrialName", "StimType", "WordGroup", "TargetWord",
    "TargetImage", "DistractorImage", "ImageL", "ImageR", 
    "FamiliarImage", "UnfamiliarImage", 
    "Audio", "Attention", "InterpolationWindow",
    # trial events
    "ImageOnset",
    "FixationOnset", "FixationDur", 
    "CarrierOnset", "CarrierEnd",
    "TargetOnset", "TargetEnd", 
    "AttentionOnset", "AttentionEnd")


```

