---
title: "Comparison of word recognition performance in native versus unfamiliar dialects for preschool age children"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(
  warning = FALSE,
  collapse = TRUE, 
  comment = "#>", 
  message = FALSE,
  fig.width = 8,
  # fig.height = 6,
  fig.asp = 0.618,
  dpi = 300,
  out.width = "80%")

wd <- rprojroot::find_rstudio_root_file()
opts_knit$set(root.dir = wd)
```

## Problem statement

ME would like to look at the data for the RWL task for participants in the
Dialect Switch study. I will 

* summarize child-level measurements for the participants in these studies
* wrangle and reduce the eyetracking data 
* plot the main effect of dialect on familiar word recognition


## Find the eyetracking blocks

Connect to database:

```{r}
library(dplyr)
library(L2TDatabase)

# Work relative to RStudio project
wd <- rprojroot::find_rstudio_root_file()
dir_here <- file.path(wd, "inst", "analyses", "ci_matching")
cnf_file <- file.path(wd, "inst", "l2t_db.cnf")

# Connect to the individual databases
l2t_main <- l2t_connect(cnf_file, "l2t")
l2t_backend <- l2t_connect(cnf_file, "backend")
l2t_eyetracking <- l2t_connect(cnf_file, "eyetracking")
```

### Determine which blocks of RWL used which stimuli

JE says that we should only use the experiments that used the re-recorded 
stimuli for TimePoint2. We modified the stimuli at TimePoint2 so that the two
dialect versions had similar durations.

These are the tables in the eyetracking database.

```{r}
src_tbls(l2t_eyetracking)
```

Tables with `q_` at the front are queries which contain helpful information
(like Study and ResearchID) alongside the main data in the table. We use the
`q_TrialAttributesByStudy` table to get information about each eyetracking 
trial.

```{r}
# Get the audio information from trial attributes. TargetEnd marks the offset of
# the wav file.
rwl_trials_attrs <- tbl(l2t_eyetracking, "q_TrialAttributesByStudy") %>% 
  filter(Task == "RWL", TrialAttribute_Name %in% c("Audio", "TargetEnd")) %>% 
  collect(n = Inf)

# Figure out the stimuli used for TP1, TP2, TP3
target_lengths <- rwl_trials_attrs %>% 
  # Convert wide to long and remove duplicate rows to get one row per audio file
  tidyr::spread(TrialAttribute_Name, TrialAttribute_Value) %>% 
  select(Study, Audio, TargetEnd) %>% 
  distinct() %>% 
  na.omit() %>% 
  # Extract dialect and keep only rows from longitudinal studies
  mutate(Dialect = substr(Audio, 1, 3)) %>% 
  select(Study, Dialect, Audio, TargetEnd) %>% 
  filter(Study %in% c("TimePoint1", "TimePoint2", "TimePoint3"))
target_lengths
```

It looks like TP1 SAE stimuli were uniformly 816 ms long and the AAE ones were
567 ms. We can use this fact to label blocks as using TP1 stimuli or not.

```{r}
# Get the audio file info for each block, figure out the stimuli used
block_stim <- rwl_trials_attrs %>% 
  tidyr::spread(TrialAttribute_Name, TrialAttribute_Value) %>% 
  select(BlockID, TrialID, Study, Audio, TargetEnd) %>% 
  na.omit() %>% 
  mutate(Dialect = substr(Audio, 1, 3)) %>% 
  # If the durations in a block are all the same and equal to one of the TP1
  # durations, mark it as TP1.
  group_by(BlockID) %>% 
  mutate(StimSet = ifelse(Dialect == "SAE" & all(TargetEnd == 816), 
                          "TP1", "Not TP1"), 
         StimSet = ifelse(Dialect == "AAE" & all(TargetEnd == 567), 
                          "TP1", StimSet)) %>% 
  ungroup() %>% 
  select(BlockID, Study, Dialect, StimSet) %>% 
  distinct() %>% 
  arrange(BlockID)
block_stim
```

Count the number of blocks with each type of stimuli in the dialect-varying
studies.

```{r}
# Check that dialect switch got 2 different sets of stimuli
block_stim %>% 
  filter(Study == "DialectSwitch") %>% 
  count(Dialect, StimSet) %>% 
  rename(nBlocks = n) %>% 
  ungroup()

block_stim %>% 
  filter(Study == "MaternalEd") %>% 
  count(Dialect, StimSet) %>% 
  rename(nBlocks = n) %>% 
  ungroup()
```

Now, we can identify which blocks got TP2 versions of the RWL experiment.



## Download block and child demographic information

Download the records for the blocks of the RWL experiment.

```{r}
# Get the dialects of each block from the table of block attributes
block_dialects <- tbl(l2t_eyetracking, "BlockAttributes") %>% 
  select(-BlockAttributeID, -BlockAttribute_Timestamp) %>% 
  collect() %>% 
  # Convert from long to wide format
  tidyr::spread(BlockAttribute_Name, BlockAttribute_Value) %>% 
  select(BlockID, Dialect)

# Get the block information (child, date, filename) for the RWL task
rwl_blocks <- tbl(l2t_eyetracking, "Blocks") %>% 
  select(-Block_Timestamp) %>% 
  filter(Block_Task == "RWL") %>% 
  collect() %>% 
  inner_join(block_dialects) %>% 
  left_join(block_stim)
rwl_blocks
```

Download child-level information.

```{r}
child_info <- tbl(l2t_backend, "Child") %>% 
  left_join(tbl(l2t_backend, "ChildStudy")) %>% 
  left_join(tbl(l2t_backend, "Study")) %>% 
  collect() %>% 
  left_join(collect(tbl(l2t_main, "Maternal_Education"))) %>% 
  select(Study, ResearchID = ShortResearchID, ChildID, ChildStudyID, 
         Female, AAE, LateTalker, CImplant, 
         Maternal_Education, Maternal_Education_Level) %>% 
  collect()
child_info
```


Attach research IDs and study names to the non-TP1 blocks.

```{r}
tp2_stim_rwl_blocks <- rwl_blocks %>% 
  left_join(child_info) %>% 
  filter(StimSet == "Not TP1") %>% 
  rename(BlockDialect = Dialect)
```

Now we count the number of dialects presented to each child to find out who
received more than one version of the experiment.

```{r}
children_who_got_multiple_dialects <- tp2_stim_rwl_blocks %>% 
  select(ChildID, AAE, BlockDialect) %>% 
  distinct() %>% 
  # Count the dialects presented to each child. Find multiple dialect children
  count(AAE, ChildID) %>% 
  filter(n > 1) %>% 
  ungroup() %>% 
  select(ChildID)

medu_scheme <- data_frame(
  Maternal_Education_Level = c(NA, 1:7),
  Maternal_Education_Group = c(NA, "Low", "Low", "Low", "Mid", 
                               "Mid", "High", "High")
)

blocks_to_keep <- tp2_stim_rwl_blocks %>% 
  inner_join(children_who_got_multiple_dialects) %>% 
  left_join(medu_scheme) %>% 
  filter(Study %in% c("DialectSwitch", "MaternalEd")) %>% 
  select(Study, ResearchID, BlockDialect, Block_Age,
         BlockID, ChildStudyID, ChildID:Maternal_Education_Group) %>% 
  mutate(
    Dialect = ifelse(AAE, "AAE", "MAE"),
    Gender = ifelse(Female, "Girl", "Boy")) 

blocks_to_keep$Maternal_Education_Group <- factor(
  blocks_to_keep$Maternal_Education_Group, 
  levels = c("Low", "Mid", "High")
)
```

One child apparently got three blocks. Figure out which block to manually
exclude.

```{r}
# Download the trial id's
rwl_trials <- tbl(l2t_eyetracking, "q_TrialsByStudy") %>% 
  filter(Task == "RWL") %>% 
  collect()

three_blocks <- rwl_trials %>% 
  inner_join(blocks_to_keep) %>% 
  distinct(Study, ResearchID, BlockID, DateTime) %>% 
  count(ResearchID) %>% 
  filter(n > 2)

rwl_trials %>% 
  inner_join(blocks_to_keep) %>% 
  semi_join(three_blocks) %>% 
  distinct(Study, ResearchID, BlockID, BlockDialect, DateTime)

# Skip the latest redundant plock
blocks_to_keep <- blocks_to_keep %>% 
  filter(BlockID != 1231)
```




## Summarize child-level information

Now that we know which blocks to include, we can get the vocabulary scores for
the children who contributed those blocks.

```{r}
evt <- tbl(l2t_main, "EVT") %>% 
  select(Study, ResearchID, EVT_Age:EVT_Standard) %>% 
  collect()

ppvt <- tbl(l2t_main, "PPVT") %>% 
  select(Study, ResearchID, PPVT_Age:PPVT_Standard) %>% 
  collect()

child_vars <- blocks_to_keep %>% 
  select(Study, ResearchID, ChildStudyID, Female:Gender) %>% 
  distinct()%>% 
  inner_join(evt) %>% 
  inner_join(ppvt)
```

Boys/girls by native dialect.

```{r}
child_vars %>% 
  count(Dialect, Gender) %>% 
  ungroup() %>% 
  rename(`N Children` = n) %>% 
  knitr::kable()
```

Maternal education by native dialect.

```{r}
child_vars %>% 
  count(Dialect, Maternal_Education_Group) %>% 
  ungroup() %>% 
  rename(`N Children` = n) %>%   
  knitr::kable() 

child_vars %>% 
  count(Dialect, Maternal_Education_Group) %>% 
  ungroup() %>% 
  tidyr::spread(Dialect, n) %>% 
  knitr::kable()

child_vars %>% 
  count(Dialect, Maternal_Education_Group, Maternal_Education) %>% 
  ungroup() %>% 
  tidyr::spread(Dialect, n) %>% 
  tidyr::replace_na(list(AAE = 0, MAE = 0)) %>% 
  knitr::kable()
```


Child level measures by dialect group.

```{r}
child_vars %>% 
  group_by(Dialect) %>% 
  summarise(
    `N Children` = n(), 
    `Mean Age (months)` = mean(EVT_Age),
    `SD Age (months)` = sd(EVT_Age),
    `N EVT` = sum(!is.na(EVT_Raw)), 
    `Mean EVT Standard` = mean(EVT_Standard),
    `SD EVT Standard` = sd(EVT_Standard),
    `N PPVT` = sum(!is.na(PPVT_Raw)), 
    `Mean PPVT Standard` = mean(PPVT_Standard),
    `SD PPVT Standard` = sd(PPVT_Standard)) %>% 
  knitr::kable(digits = 1)


child_vars %>% 
  group_by(Maternal_Education_Group) %>% 
  summarise(
    `N Children` = n(), 
    `Mean Age (months)` = mean(EVT_Age),
    `SD Age (months)` = sd(EVT_Age),
    `N EVT` = sum(!is.na(EVT_Raw)), 
    `Mean EVT Standard` = mean(EVT_Standard),
    `SD EVT Standard` = sd(EVT_Standard),
    `N PPVT` = sum(!is.na(PPVT_Raw)), 
    `Mean PPVT Standard` = mean(PPVT_Standard),
    `SD PPVT Standard` = sd(PPVT_Standard)) %>% 
  knitr::kable(digits = 1)
```




## Download the gaze data

Download the eyetracking data

```{r}
# Download the gazes
raw_rwl_looks <- tbl(l2t_eyetracking, "Looks") %>% 
  select(TrialID, Time, GazeByImageAOI) %>% 
  collect(n = Inf) %>% 
  inner_join(rwl_trials)

rwl_looks <- raw_rwl_looks %>% 
  inner_join(blocks_to_keep) 

rwl_looks <- rwl_looks %>% 
  left_join(child_vars) %>% 
  select(Study, ResearchID, Dialect, BlockDialect, Block_Age,
         BlockID, ChildID:Maternal_Education_Level, 
         Maternal_Education_Group:PPVT_Standard,
         TrialID, TrialNo, Time, GazeByImageAOI)

rwl_looks <- rwl_looks %>% 
  mutate(
    BlockDialect = ifelse(BlockDialect == "AAE", "AAE", "MAE"),
    HearsNativeDialect = Dialect == BlockDialect)
```



## Data screening

Excessive missing data is defined as having more than 50% missing data between 0
and 2000 ms (relative to target onset).

Filter out participants who have an *entire block* with excessive missing data
averaged across trials.

```{r}
library(lookr)
library(ggplot2)

participants_to_drop <- rwl_looks %>% 
  filter(between(Time, 0, 2005)) %>% 
  AggregateLooks(Dialect + BlockID + ResearchID ~ GazeByImageAOI) %>%
  tibble::as_tibble() %>% 
  filter(PropNA > .5) %>% 
  select(NativeDialect = Dialect, ResearchID)

participants_to_drop
```

`r nrow(participants_to_drop)` participants are dropped for excessive
missing data.

Filter out individual trials with excessive missing data.

```{r}
trials_to_drop  <- rwl_looks %>% 
  anti_join(participants_to_drop) %>% 
  filter(between(Time, 0, 2005)) %>%
  AggregateLooks(Dialect + TrialID + ResearchID ~ GazeByImageAOI) %>% 
  tibble::as_tibble() %>% 
  filter(PropNA > .5) %>% 
  select(NativeDialect = Dialect, ResearchID, TrialID)

trials_to_drop %>% 
  count(NativeDialect)
```

`r nrow(trials_to_drop)` additional trials are dropped.


Data quality stats for remaining children.

```{r}
rwl_looks %>%
  anti_join(participants_to_drop) %>% 
  anti_join(trials_to_drop) %>% 
  filter(between(Time, 0, 2005)) %>% 
  AggregateLooks(Dialect + ResearchID + TrialID ~ GazeByImageAOI) %>% 
  tibble::as_tibble() %>% 
  group_by(Dialect, ResearchID) %>% 
  summarise(
    nGoodTrials = n(),
    Mean_Prop_NA = mean(PropNA)) %>% 
  summarise(
    nChildren = n(), 
    `Total Useable Trials` = sum(nGoodTrials),
    `Mean N of Useable Trials` = mean(nGoodTrials) %>% round(1), 
    `SD Trials` = sd(nGoodTrials) %>% round(1),
    `Min Trials` = min(nGoodTrials),
    `Max Trials` = max(nGoodTrials),
    `Mean Prop of Missing Data` = mean(Mean_Prop_NA) %>% round(3), 
    `SD Prop Missing` = sd(Mean_Prop_NA) %>% round(3),
    `Min Prop Missing` = min(Mean_Prop_NA) %>% round(3),
    `Max Prop Missing` = max(Mean_Prop_NA) %>% round(3)) %>% 
  knitr::kable()
```


## Finally, plots of fixation patterns over time

Aggregated looking data over Time across trials within Dialect x BlockDialect
within Child.

```{r}
looks <- rwl_looks %>%
  anti_join(participants_to_drop) %>% 
  anti_join(trials_to_drop) %>% 
  filter(between(Time, -505, 2005)) %>% 
  AggregateLooks(Maternal_Education_Group + Study + Dialect + BlockDialect + 
                   HearsNativeDialect + ResearchID + Time ~ GazeByImageAOI) %>% 
  tibble::as_tibble() %>% 
  mutate(Looks_Images = Target + Others,
       Prop_Target = Target / Looks_Images,
       Prop_PhonologicalFoil = PhonologicalFoil / Looks_Images,
       Prop_SemanticFoil = SemanticFoil / Looks_Images,
       Prop_Unrelated = Unrelated / Looks_Images)

evt <- child_vars %>% 
  mutate(Vocab3tile = ntile(EVT_Standard, 3), 
         `Exp. vocab.` = factor(Vocab3tile, 1:3, 
                                c("Lower third", "Middle third", "Upper third"))) %>% 
  select(Study, ResearchID, Vocab3tile, `Exp. vocab.`)

looks <- looks %>% 
  mutate(`Child hears` = ifelse(HearsNativeDialect, "Native dialect", 
                                "Non-native dialect"),
         `Native dialect` = Dialect,
         `Maternal edu.` = Maternal_Education_Group) %>% 
  left_join(evt)

```


```{r gca-plots}
library(hrbrthemes)
plot_text <- list(
  x_time = "Time (ms) after target noun onset", 
  y_target = "Proportion of looks to named image",
  y_image = "Proportion of looks to image",
  caption_mean_se = "Mean ± SE"
)

ggplot(looks) + 
  aes(x = Time, y = Proportion) +   
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  geom_vline(xintercept = 0, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  theme_ipsum_rc(axis_title_size = 11) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target, 
       caption = plot_text$caption_mean_se)

ggplot(looks) + 
  aes(x = Time, y = Proportion, color = `Child hears`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  geom_vline(xintercept = 0, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target)

ggplot(looks) + 
  aes(x = Time, y = Proportion, color = `Child hears`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target) +
  facet_wrap("`Native dialect`", labeller = label_both) + 
  xlim(0, 2000)

ggplot(looks %>% filter(!is.na(Maternal_Education_Group))) + 
  aes(x = Time, y = Proportion, color = `Child hears`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target) +
  facet_wrap("`Maternal edu.`", labeller = label_both) + 
  xlim(0, 2000)

ggplot(looks %>% filter(!is.na(`Exp. vocab.`))) + 
  aes(x = Time, y = Proportion, color = `Child hears`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target) +
  facet_wrap("`Exp. vocab.`", labeller = label_both) + 
  xlim(0, 2000)
```

## Plot looks to each competitor type.

```{r aoi-plots}
df_looks_to_aois <- looks %>% 
  select(Study, ResearchID, `Child hears`:`Maternal edu.`, `Exp. vocab.`,
         Time, starts_with("Prop_")) %>% 
  tidyr::gather(AOI, Proportion, starts_with("Prop_")) %>% 
  mutate(AOI = AOI %>% 
           stringr::str_replace("Prop_", "") %>% 
           stringr::str_replace("Foil", "")) 

df_looks_to_aois$AOI <- factor(
  df_looks_to_aois$AOI, 
  levels = c("Target", "Phonological", "Semantic", "Unrelated"))

df_looks_to_aois$Image <- factor(
  df_looks_to_aois$AOI, 
  labels = c("Target word", "Phonological foil", "Semantic foil", "Unrelated word"),
  levels = c("Target", "Phonological", "Semantic", "Unrelated"))


ggplot(df_looks_to_aois) + 
  aes(x = Time, y = Proportion, color = Image) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)

ggplot(df_looks_to_aois) + 
  aes(x = Time, y = Proportion, color = Image) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  facet_wrap("`Child hears`", labeller = label_both) + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)
```

By AOI

```{r by-aoi}
ggplot(df_looks_to_aois %>% filter(Image == "Phonological foil")) + 
  aes(x = Time, y = Proportion, color = `Child hears`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  facet_wrap("Image") + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)

# Use %+% to replace the data-set used in a plot
last_plot() %+% 
  filter(df_looks_to_aois, Image == "Semantic foil")

last_plot() %+% 
  filter(df_looks_to_aois, Image == "Unrelated word")

last_plot() %+% 
  filter(df_looks_to_aois, Image == "Target word")
```

AOI by maternal edu

```{r aoi-by-medu}
ggplot(df_looks_to_aois %>% 
         filter(Image == "Phonological foil", !is.na(`Maternal edu.`))) + 
  aes(x = Time, y = Proportion, color = `Maternal edu.`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  facet_wrap("Image") + 
  theme_ipsum_rc(axis_title_size = 11) + 
  viridis::scale_color_viridis(discrete = TRUE, option = "inferno", end = .9) +
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)

last_plot() %+% 
  filter(df_looks_to_aois, 
         Image == "Semantic foil", !is.na(`Maternal edu.`))

last_plot() %+% 
  filter(df_looks_to_aois, 
         Image == "Unrelated word", !is.na(`Maternal edu.`))

last_plot() %+% 
  filter(df_looks_to_aois, 
         Image == "Target word", !is.na(`Maternal edu.`))


ggplot(df_looks_to_aois %>% filter(!is.na(`Maternal edu.`))) + 
  aes(x = Time, y = Proportion, color = `Maternal edu.`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary(fun.y = "mean", geom = "line", size = 1.5) + 
  viridis::scale_color_viridis(discrete = TRUE, option = "inferno", end = .9) +
  facet_wrap("Image") + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)


ggplot(df_looks_to_aois) + 
  aes(x = Time, y = Proportion, color = `Native dialect`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary(fun.y = "mean", geom = "line", size = 1.5) + 
  viridis::scale_color_viridis(discrete = TRUE, option = "viridis", end = .9) +
  facet_wrap("Image") + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)

ggplot(df_looks_to_aois) + 
  aes(x = Time, y = Proportion, color = `Child hears`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  facet_wrap("AOI", labeller = label_both) + 
  theme_ipsum_rc(axis_title_size = 11) + 
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target) + 
  xlim(0, 2000)


```

```{r by-vocabulary}
ggplot(df_looks_to_aois %>% 
         filter(Image == "Phonological foil", !is.na(`Exp. vocab.`))) + 
  aes(x = Time, y = Proportion, color = `Exp. vocab.`) + 
  geom_hline(yintercept = .25, size = 1.25, color = "#cccccc") + 
  stat_summary() + 
  facet_wrap("Image") + 
  theme_ipsum_rc(axis_title_size = 11) + 
  viridis::scale_color_viridis(discrete = TRUE, option = "plasma", end = .9) +
  theme(legend.position = "bottom", legend.text = element_text(size = 10)) + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_image) + 
  xlim(0, 2000)

last_plot() %+% 
  filter(df_looks_to_aois, 
         Image == "Semantic foil", !is.na(`Exp. vocab.`))

last_plot() %+% 
  filter(df_looks_to_aois, 
         Image == "Unrelated word", !is.na(`Exp. vocab.`))

last_plot() %+% 
  filter(df_looks_to_aois, 
         Image == "Target word", !is.na(`Exp. vocab.`)) 

```

